% !TEX root = root.tex
% 

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
%\documentclass[a4paper, 10pt, conference]{ieeeconf}

\input{latex_common/preamble.tex}
\input{latex_common/my_tikz.tex}
\input{special.tex}

\IEEEoverridecommandlockouts                              % This command is only needed if                                                         % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf Title
}


\author{Taylor P. Reynolds and Mehran Mesbahi% <-this % stops a space
\thanks{*This research has been supported by XXX}% <-this % stops a space
\thanks{The authors are with the W.E. Boeing Department of Aeronautics and Astronautics,
        University of Washington, Seattle, WA, USA.
        {\tt\small \{tpr6,mesbahi\}@uw.edu}}%
% \thanks{$^{2}$Bernard D. Researcher is with the FacultyDepartment of Electrical Engineering, Wright State University,
%         Dayton, OH 45435, USA
%         {\tt\small b.d.researcher@ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

abstract.

\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

The point of this paper is to communicate the ``creeping phenonmenon'' that occurs in sequential convex programming algorithms that are designed a certain way. It seems to be a fundamental limitation of a certain class of algorithms. 

\begin{itemize}
\item what is the purpose of the paper?
\item why is this important, and how is it useful?
\end{itemize}

\section{SEQUENTIAL CONVEX PROGRAMMING}

\begin{itemize}
\item provide an overview of SCP methods, similar to a condensed version of CSM.
\item provide a generalized algorithmic framework for the class of algorithms susceptible to the creeping phenomenon.
\end{itemize}
% only go so far as to define the linear and nonlinear costs as "original cost" plus "feasibility measure". 

Consider the following optimization problem
\begin{subequations}\label{eq:nlp}
\begin{align}
\min_z &\quad \ocost(\z) \label{eq:nlp_a} \\
\text{subject to:} &\quad g_i(\z) \leq 0, \quad i \in \setIcvx \label{eq:nlp_b}\\
&\quad h_i (\z) \leq 0, \quad i \in \setIncvx \label{eq:nlp_c}
\end{align}
\end{subequations}
where $\z\in\real^{\nz}$, $\setIcvx = \{1,\ldots,n_i\}$, $\setIncvx=\{n_i+1,\ldots,n_i+n_e\}$ represent the indices of the convex and non-convex inequality constraints respecitvely. We shall assume that the cost function $\ocost$ is convex, and that each $h_i$ is at least once differentiable almost everywhere. To simplify the notation, we assume that any equality constraints are represented by a pair of inequality constraints. Problem~\eqref{eq:nlp} is typically refered to as a nonlinear programming problem, but herein we shall refer to it as the original non-convex optimization problem (or simple the original problem). While there exist general purpose solvers that are able to solve the original problem (see, e.g.,~\cite{Gill1981,NocedalWright}), a current trend is to seek solutions by using iterative schemes that are based on convex optimization. 

The barrier to directly applying convex optimization methods is of course the set of non-convex constraints~\eqref{eq:nlp_c}. Sequential convex programming methods approximate each constraint in~\eqref{eq:nlp_c} with a convex function of the solution variable. Each convex approximation is computed using a reference solution, $\zb$, and takes the form
\begin{equation}
\bar{h}_i(\z,\zb) \leq 0, \quad i\in\setIncvx.
\label{eq:cvx_approximation_general}
\end{equation}
There are several choices for $\bar{h}_i$: first- or second-order Taylor series approximations, inner convex approximations, or any other convex function that locally approximates the non-convex $h_i$. These approximations are inherently local; they accuracy decreases as $\|\z-\zb\|$ increases. In addition, consider the possible scenario where $\ocost$ and each $g_i$ are linear functions, and we choose each $\bar{h}_i$ to be a first-order approximation (i.e. the linearization of $h_i$ around $\zb$). In this case, the resulting optimization problem is unbounded below, a phenomenon refered to as \textit{artificial unboundedness}. To address the local nature of the approximations~\eqref{eq:cvx_approximation_general} and to avoid artificial unboundedness, we add a \textit{trust region} constraint of the form
\begin{equation}
\| \z - \zb \|_q \leq \eta,
\label{eq:trust_region}
\end{equation}
where $q=\{1,\,2,\,\infty\}$ and $\eta\in\realpp$ is a positive \textit{trust region radius}. Now we may formulate the following convex approximation to Problem~\eqref{eq:nlp}:
\begin{subequations}\label{eq:cvx_tr}
\begin{align}
\min_z &\quad \ocost(\z) \label{eq:cvx_tr_a} \\
\text{subject to:} &\quad g_i(\z) \leq 0, \quad i\in\setIcvx \label{eq:cvx_tr_b} \\
&\quad \bar{h}_i(\z,\zb) \leq 0, \quad i\in\setIncvx \label{eq:cvx_tr_c}\\
&\quad \| \z - \zb \|_q \leq \eta  \label{eq:cvx_tr_d}
\end{align}
\end{subequations}
Problem~\eqref{eq:cvx_tr} is now a convex program. However, directly solving Problem~\eqref{eq:cvx_tr} has proved difficult in several previous studies \todo{add studies}. In particular, Problem~\eqref{eq:cvx_tr} is susceptible to \textit{artificial infeasibility} that stems from two probable causes. First, the approximation~\eqref{eq:cvx_tr_c} and trust region~\eqref{eq:cvx_tr_d} can be incompatible, in the sense that $\mathcal{F}_1 = \{\z\,|\,\eqref{eq:cvx_tr_c}\text{ and }\eqref{eq:cvx_tr_d}\text{ are satisfied}\} = \emptyset$. This occurs when the reference $\zb$ is further than a distance $\eta$ from the set $\{\z\,|\,h_i(\z)\leq,~i\in\setIcvx\}$ under the $q$-norm. Second, the constraints~\eqref{eq:cvx_tr_b} and~\eqref{eq:cvx_tr_c} can be incompatible, in the sense that $\mathcal{F}_2 = \{\z\,|\,\eqref{eq:cvx_tr_b}\text{ and }\eqref{eq:cvx_tr_c}\text{ are satisfied}\}=\emptyset$. Each of these cases are pictured in~\todo{add figure from CSM}. Artificial infeasibility can be avoided by adding so-called \textit{virtual control} to~\eqref{eq:cvx_tr_c}:
\begin{equation}
\bar{h}_i(\z,\zb) - \vc_i \leq 0
\end{equation}
where $\vc_i > 0$. The vector $\vc\in\real^{n_e}$ is added as a solution variable, and the resulting augmented convex program is
\begin{subequations}\label{eq:cvx_apprx}
\begin{align}
\min_{\z,\vc} &\quad \ocost(\z) + \lambda P(\nu) \label{eq:cvx_apprx_a} \\
\text{subject to:} &\quad g_i(\z) \leq 0, \quad i\in\setIcvx \label{eq:cvx_apprx_b} \\
&\quad \bar{h}_i(\z,\zb) - \vc_i \leq 0, \quad i\in\setIncvx \label{eq:cvx_apprx_c}\\
&\quad \|\z-\zb\|_q \leq \eta \label{eq:cvx_apprx_d}
\end{align}
\end{subequations}
where $P : \real^{n_e} \rightarrow \realpp$ is a positive-definite penalty function and $\lambda>0$ is a user-selected weight. Typically $\lambda \gg 1$ to limit the use of virtual control only to cases when it is required to avoid artificial infeasibility.

We shall refer to a solution to Problem~\eqref{eq:cvx_apprx} as an \textit{iterate}, and denote it by $(\z^*,\vc^*)$. Sequential convex programming algorithms iteratively solve Problem~\eqref{eq:cvx_apprx} and use resulting iterate to update $\zb$. The resulting sequence of solutions $\zb$ approaches a locally optimal solution of~\eqref{eq:nlp} under certain conditions and problem assumptions. There have been numerous papers that study the convergence properties of these algorithms, offering conditions/assumptions under which convergence is guaranteed~\todo{add citations}. This paper does not discuss \textit{whether} convergence is achieved or at what rate, but is instead focused on \textit{how} the iterates are related to each other.

\subsection{Trust Region Updates}

The convergence process is guided by the size of the trust region radius $\eta$. The radius is updated based on a metric that measures the accuracy of the approximations~\eqref{eq:cvx_approximation_general}. To this end, we define the following functions
\begin{subequations}
\begin{align}
J(\z) = \ocost(\z) + \lambda P(h(\z)) \\
L(\z) = \ocost(\z) + \lambda P(\vc)
\end{align}
\end{subequations}
where $h(\z) \in \real^{n_e}$ is the concatenation of the non-convex constraints from the original problem~\eqref{eq:nlp_c}.

\section{THE CREEPING PHENOMENON}

% introduce two ways of computing the progress metric; dJ/dL and dL/L. Both are susceptible to creeping.
\begin{itemize}
\item introduce the creeping phenomenon, provide a graphical description
\item include an example of what this can look like
\end{itemize}


\section{POSSIBLE REMEDIES: HYBRID ALGORITHMS}

\begin{itemize}
\item discuss possible remedies; if we know we have a feasible start, what can we do?
\item soft trust region methods?
\end{itemize}

\section{CONCLUSIONS}


% \addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{APPENDIX}

% Appendixes should appear before the acknowledgment.

% \section*{ACKNOWLEDGMENT}

% The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ. Avoid the stilted expression, ÒOne of us (R. B. G.) thanks . . .Ó  Instead, try ÒR. B. G. thanksÓ. Put sponsor acknowledgments in the unnumbered footnote on the first page.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{thebibliography}{99}

% \bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
% \bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
% \bibitem{c5} E. H. Miller, ÒA note on reflector arrays (Periodical styleÑAccepted for publication),Ó IEEE Trans. Antennas Propagat., to be publised.
% \bibitem{c6} J. Wang, ÒFundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),Ó IEEE J. Quantum Electron., submitted for publication.
% \bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
% \bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ÒElectron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),Ó IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740Ð741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
% \bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
% \bibitem{c10} J. U. Duncombe, ÒInfrared navigationÑPart I: An assessment of feasibility (Periodical style),Ó IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
% \bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ÒA clustering technique for digital communications channel equalization using radial basis function networks,Ó IEEE Trans. Neural Networks, vol. 4, pp. 570Ð578, July 1993.
% \bibitem{c12} R. W. Lucky, ÒAutomatic equalization for digital communication,Ó Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
% \bibitem{c13} S. P. Bingulac, ÒOn the compatibility of adaptive controllers (Published Conference Proceedings style),Ó in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8Ð16.
% \bibitem{c14} G. R. Faulhaber, ÒDesign of service systems with priority reservation,Ó in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
% \bibitem{c15} W. D. Doyle, ÒMagnetization reversal in films with biaxial anisotropy,Ó in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
% \bibitem{c16} G. W. Juette and L. E. Zeffanella, ÒRadio noise currents n short sections on bundle conductors (Presented Conference Paper style),Ó presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
% \bibitem{c17} J. G. Kreifeldt, ÒAn analysis of surface-detected EMG as an amplitude-modulated noise,Ó presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
% \bibitem{c18} J. Williams, ÒNarrow-band analyzer (Thesis or Dissertation style),Ó Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
% \bibitem{c19} N. Kawasaki, ÒParametric study of thermal and chemical nonequilibrium nozzle flow,Ó M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
% \bibitem{c20} J. P. Wilkinson, ÒNonlinear resonant circuit devices (Patent style),Ó U.S. Patent 3 624 12, July 16, 1990. 

% \end{thebibliography}

\bibliographystyle{ieeetr}
\bibliography{references}


\end{document}
